Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 result_discussion.tex
finished pass through Section 3

\section{Overview of Results and Discussion}
\dkcomment{I envision this section doing the following:
\begin{enumerate}
\item State the main theorem(s) formally.
\item Discuss lower bounds or impossibility results.
\item Discuss extensions.
\item Discuss the justification or comparison to standard bandits.
\item Discuss the comparison in the 2x2 square.
\end{enumerate}
}

\dkcomment{For now, I am just copying over material from various other
  parts that Bangrui/Peter wrote or I had written in earlier
  iterations.}

\dkcomment{In the results discussion clarify which results need to
  know $T$ and which don't.}

\begin{theorem} \label{thm:main-overview}
Under some technical assumptions, 
there exists a policy which pays at most $O(\ARMNUM^2)$ in expectation,
and achieves regret at most $O(\ARMNUM^2 + \log^2(T))$.
\dkcomment{Omitting the density here.}
\end{theorem}

As we discuss in more detail in Section~\ref{sec:main-discussion},
the reason we obtain stronger regret bounds than in the standard bandit
setting is that the agents' heterogeneity in preferences will
naturally lead to exploration.

Here we pursue an alternate direction to our analysis of incentivizing exploration with heterogeneous preferences: we consider approximation-style results comparing achievable algorithm performance across four different problem settings, described in the table below.

\begin{center}
\begin{tabular}{ c|c|c| } 
 \hline
     & Pulls arms directly & Needs to incentivize \\ 
\hline
 Perfect Info on Preferences & $C11$: The ``God'' Policy & $C12$ \\ 
 Partial Info on Preferences & $C21$ & $C22$: actual algorithm \\ 
 \hline
\end{tabular}
\end{center}

Columns indicate whether the principal pulls arms directly (left column) or incentivizes agents who in turn actually pull the arms. Rows indicate whether the principal knows the preferences of the agents (top row) or not (bottom row).   Problem settings correspond to cells and are described by the names C11, C12, and so on. An optimal algorithm for problem setting C11 has the best performance possible.

We wish to make two high-level points through this analysis:

\begin{itemize}
\item First, better performance is possible in setting C22 than in setting C21, in the sense we can find tight approximation guarantees relative to C11 that are better for C22 than for C21.  This is achieved by setting up incentives in C22 that still allow agents to select arms aligned with their preferences, providing selections of arms that contain more information than in C21.
\item Second, heterogeneity in preferences improves performance over what can be achieved in a setting with homogeneous preferences.  This would be in the spirit of David K.'s results that heterogeneity in preference for money can be exploited to reduce the budget required.
\end{itemize}

Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.

>>>>

\section{Overview of Results and Discussion}

Our main algorithm is presented as
Algorithm~\ref{alg:basic-incentivizing}
in Section~\ref{sec:ub}.
Our main result is the following pair of theorems%
\footnote{Recall that we omit the dependence on parameters other than
  \ARMNUM, \MinProb, $T$ unless making a particular point.},
analyzing the payments and regret of the algorithm.

\begin{theorem} \label{rst:budget}
The expected total payment of
Algorithm~\ref{alg:basic-incentivizing} is at most
$O \left(\ARMNUM^2 \cdot \e^{2/\MinProb} \right)$.
\end{theorem}

\begin{theorem} \label{rst:regret}
For any time horizon $T$, the expected cumulative regret for
Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
above by 
$O \left(\ARMNUM \cdot \e^{2/\MinProb} + \TieDensity \ARMNUM \log^3(T) \right)$.
\end{theorem}

When $\TieDensity = 0$, the bound of Theorem~\ref{rst:regret} is
constant in $T$;
thus, the algorithm achieves constant regret for constant payment. 
The case $\TieDensity = 0$ arises, for instance, in the case of a
discrete distribution for agents.
In fact, in the case of a discrete distribution of agents,
it is possible to modify the algorithm to reduce the dependence on
\MinProb from exponential to polynomial.
Theorem~\ref{rst:discrete} (given later) states that the modified
algorithm achieves expected regret
$O \left(\frac{\ARMNUM}{\MinProb^4} \right)$
with expected payments of
$O \left(\frac{\ARMNUM^2}{\MinProb^{5/2}} \right)$.

The fact that constant regret can be achieved with constant payment
(independent of $T$) when $\TieDensity = 0$ suggests aiming for a
constant bound more generally, i.e., for $\TieDensity > 0$.
That such a bound is unachievable is shown in Section~\ref{sec:lb},
where we show a lower bound of $\Omega(\log(T))$ on
the expected regret of any algorithm.
The instance is very simple: it has two arms, one of which has known
attributes; in addition, one draw from the other arm is observed in
each step $t$ even when it is not pulled.
While the probability of pulling the wrong arm decreases over time, it
does not do so fast enough, causing the stated regret.

The exponential dependence on $1/\MinProb$ implies an exponential
dependence on \ARMNUM (because $\MinProb \leq 1/\ARMNUM$).
This exponential dependence arises from a need to continue to
incentivize arm pulls to ensure that nearly tied agents learn their
best arms quickly.
Aside from the assumption that $\TieDensity = 0$, another assumption
allows us to eliminate this exponential dependency.
Namely, when \MinProb (or a lower bound on it) is known ahead of time,
the algorithm can be modified to incentivize arms less aggressively.
As shown in Theorem~\ref{rst:known-p},
the modified algorithm will have expected regret at most
$O \left(\frac{\ARMNUM}{\MinProb^3}
+\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb} \right)$,
with expected payments of at most
$O \left(\frac{\ARMNUM^2}{\MinProb^{5/2}} \right)$.

We compare these bounds to those for standard bandits,
focusing on the dependence on $T$.  
The standard bandit setting is the case when the agent types \AgV
are concentrated on a single point, and agents pull arms at the
principal's direction without requiring payment.
(Notice that this setting violates our Assumption~\ref{A3},
so out bounds do not apply to it.)
Then, the payment is $0$ and the expected regret scales as
$\Theta(\log(T))$ \cite[Theorem 2.1]{bubeck2012regret}.

Our algorithm's payment is constant in $T$,
while its regret is $O(\log^3(T))$ in general with a lower bound of
$\Omega(\log(T))$;
when preferences are discrete, our algorithm's regret is
constant in $T$.
Thus, viewed solely in terms of the dependence on $T$,
the best performance achievable seems comparable to that in a standard
multi-armed bandit problem;
but when preferences our discrete, the constant regret (rather than
$\Theta(\log T)$ surpasses a standard multi-armed bandit.
This may seem surprising, because our setting is one in which the
principal has both less control and less information than in the
standard bandit setting.
The result arises because heterogeneity in preferences indeed provides
free exploration, in which all of the arms can be pulled infinitely
often without incurring regret.

While heterogeneity in preferences enables this free exploration,
heterogeneity alone is not always sufficient for enabling performance
improvements compare to the standard bandit setting.
Indeed, consider a version in which agents are still heterogeneous,
but the principal has the power to pull arms directly.
Unless the heterogeneity can be observed (i.e., the principal knows
the agents' types), the principal will be unable to correctly choose
each agent's preferred arm,
even with infinite exploration of arm attributes.
Hence, in this setting, the regret will grow as $\Omega(T)$.

Thus, reaping the benefits of (unobserved) heterogeneous preferences
requires the principal to give up direct control of the arms,
providing agents the autonomy they need to express their private
information about their own preferences.
Our results show that simple arm-based incentives are sufficient
to overcome the apparent challenges created by this abdication of
control.
